---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

humanparser is a very small package that parses full (human) names into their component parts. Uses code from the node.js [humanparser](https://github.com/chovy/humanparser) module.

The following functions are implemented:

- `parse_name`:	Parse a "human" name into components
- `parse_names`:	Parse a character vector of names into a data frame

### News

- Version 0.0.1.999 released - tests
- Version 0.0.0.999 released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/humanparser")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(humanparser)

# current verison
packageVersion("humanparser")

# just one

parse_name("John Smith Jr.")

# or a bunch of 'em

full_names <- c("David Regan", "Izaque Iuzuru Nagata", 
                "Christian Schmit de la Breli", "Peter Doyle", "Hans R.Bruetsch", 
                "Marcus Reichel", "Per-Axel Koch", "Louis Van der Walt", 
                "Mario Adamek", "Ugur Tozsekerli", "Judit Ludvai" )

parse_names(full_names)

```

### Test Results

```{r}
library(humanparser)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
